Pipeline Performance Figure Generation

### 2023-08-02 TestingPipeline/Scripts/paper_figure_generation_balanced_testing.Rmd
Updating the 50:50 split piece.

ggsave(
  "../IntermediaryFiles/all_MCC_scatterplot.png",
  plot = fig,
  scale = 1,
  width = 8,
  height = 4,
  units = c("in", "cm", "mm", "px"),
  dpi = 300,
  limitsize = TRUE
)

ggplot(accuracy_scores, aes(x=toolcombo, y=MCC, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=20),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("MCC") +
  scale_fill_manual(name="Number of Tools",
                     values = alpha(rev(viridis(6)), 0.5)) +
  scale_color_manual(name="Number of Tools",
                     values = alpha(rev(viridis(6)), 1))
```
```{r}
max(accuracy_scores$MCC)
```
=78

getting set of tools with roughly equivalent MCC
```{r}
t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="0 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="0 1 1 0 0 1"])

t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="0 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 0 0 1"])

t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="0 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="0 0 0 0 0 1"])

t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="0 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 1 0 1"])

t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="0 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 0 1 1"])

t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="0 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="1 1 1 0 0 1"])
```
accounting for multiple t-tests with Bonferroni, then the following have the same MCC:
- vs2+tnv, vs2+tnv+dvf, vs2, vs2+tnv+tv+vb, vs2+tnv+tv+vs

@@

pheatmap::pheatmap(as.matrix(viral_scores_1),
                  annotation_row = ann_col,
                  annotation_colors = ann_colors,
                  border_color = NA,
                  show_rownames = T,
                  show_colnames = F,
                  annotation_legend = F,
                  cluster_rows = F,
                  cluster_cols = F,
                  cellheight=3,
                  filename = "../IntermediaryFiles/heatmap_MCC_labels.png"
                  )
```

>>>>

fig

ggplot(accuracy_scores, aes(x=toolcombo, y=MCC, 
                                  color=numtools, fill=numtools)) +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=20),
  ) +
  xlab("Tool Combination (tv, DVF, tnv, VB, VS, VS2)") +
  ylab("MCC") +
  scale_fill_manual(name="Number of Tools",
                     values = alpha(rev(viridis(6)), 0.5)) +
  scale_color_manual(name="Number of Tools",
                     values = alpha(rev(viridis(6)), 1))
```

```{r}
max(accuracy_scores$MCC)
```
=91

getting set of tools with roughly equivalent MCC
```{r}
t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 0 1 1"])

t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="1 1 1 0 0 1"])

t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 1 0 1"])

t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="1 1 1 0 1 1"])

t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 1 1 1"])

t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 0 0 0 1"])

t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="1 1 1 1 0 1"])

t.test(accuracy_scores$MCC[accuracy_scores$toolcombo=="1 0 1 0 0 1"], 
       accuracy_scores$MCC[accuracy_scores$toolcombo=="1 1 1 1 1 1"])
```
accounting for multiple t-tests with Bonferroni, then the following have the same MCC:
- vs2+tnv, vs2+tnv+dvf, vs2, vs2+tnv+tv+vb, vs2+tnv+tv+vs

@@

pheatmap::pheatmap(as.matrix(viral_scores_1),
                  annotation_row = ann_col,
                  annotation_colors = ann_colors,
                  border_color = NA,
                  show_rownames = T,
                  show_colnames = F,
                  annotation_legend = F,
                  cluster_rows = F,
                  cluster_cols = F,
                  cellheight=3,
                  filename = "../IntermediaryFiles/heatmap_MCC_labels_50-50.png"
                  )
```
